Overview

### 2023-12-02 analysis/001_overview.Rmd
Publishers league table description

Analysing hybrid open access across publishers between 2018 and 2022 reveals a large concentration on a few publishers in terms of publication volume. 
While transformative agreements could be attributed to `r length(unique(publisher_plot_df$esac_publisher))` distinct publishers, the three publishers Elsevier, Springer Nature and Wiley accounted for xxx percent of articles published. Together, they published xxx articles, representing a share of xx percent. xxx were published through transformative agreements. 
The remainder consists of

@@

publisher_league_tbl <-
  inner_join(publisher_article_total_table, publisher_article_oa_table) |>
  inner_join(publisher_article_ta_oa_table)

publisher_league_tbl |>
  mutate(across(contains(c("perc", "cum")), ~ paste(round(., 3) * 100))) |>
  kbl(
    col.names = c(
      "Publisher",
      "Total",
      "%",
      "C%",
      "Total",
      "%",
      "C%",
      "Total",
      "%",
      "C%",
      "Total",
      "%",
      "C%"
    ),
    format.args = list(big.mark = ',')
  ) %>%
  kable_classic() %>%
  add_header_above(c(
    " " = 1,
    "Hybrid journals" = 3,
    "Articles" = 3,
    "OA articles" = 3,
    "TA OA articles" = 3
  ))
```

Figure 2 presents the growth of hybrid open access across publishers by year, highlighting the proportion of open articles published under transformative agreements. As can be seen from Figure 2A and 2C

>>>>

@@

publisher_league_tbl <-
  inner_join(publisher_article_total_table, publisher_article_oa_table) |>
  inner_join(publisher_article_ta_oa_table)
```

```{r}
publisher_league_tbl |>
  mutate(across(contains(c("perc", "cum")), ~ paste(round(., 3) * 100))) |>
  kbl(
    caption ="Hybrid open access through transformative agreements market shares 2018-2022",
    col.names = c(
      "Publisher",
      "Total",
      "%",
      "C%",
      "Total",
      "%",
      "C%",
      "Total",
      "%",
      "C%",
      "Total",
      "%",
      "C%"
    ),
    format.args = list(big.mark = ',')
  ) %>%
  kable_classic() %>%
  add_header_above(c(
    " " = 1,
    "Hybrid journals" = 3,
    "Articles" = 3,
    "OA articles" = 3,
    "TA OA articles" = 3
  ))
```

Analysing hybrid open access across publishers between 2018 and 2022 reveals a large market concentration among a small number of publishers. 
Although `r length(unique(jn_ind_jct_all$esac_publisher))` publishers offered transformative agreements, the three major commercial publishers Elsevier, Springer Nature, and Wiley, accounted for `r publisher_league_tbl  |> filter(publisher == "Wiley") |> pull(jn_cum) * 100`% of total article volume published (see Table ).
Together, they published `r publisher_league_tbl  |> filter(publisher != "Other") |> pull(oa_total) |> sum()` open access articles, representing `r publisher_league_tbl  |> filter(publisher == "Wiley") |> pull(oa_cum) * 100`% of the open access articles in hybrid journals.
Elsevier, Springer Nature, and Wiley made `r publisher_league_tbl  |> filter(publisher != "Other") |> pull(ta_oa_total) |> sum()` articles open access in hybrid journals through transformative agreements, resulting in an even larger market share of `r publisher_league_tbl  |> filter(publisher == "Wiley") |> pull(ta_oa_cum)*100`%.
However, there are differences among the three large publishers. Although Elsevier published the largest volume of articles (n = `r publisher_league_tbl  |> filter(publisher == "Elsevier") |> pull(publisher_total)`, `r publisher_league_tbl  |> filter(publisher == "Elsevier") |> pull(cum)*100`%), it published a relatively low number of open access articles, including those that can be associated with transformative agreements.
In contrast, Springer Nature and Wiley provided open access to a much larger proportion of their articles (`r (publisher_league_tbl  |> filter(publisher == "Springer Nature") |> pull(oa_total)) / (publisher_league_tbl  |> filter(publisher == "Springer Nature") |> pull(publisher_total)) * 100`% of Springer Nature articles and `r (publisher_league_tbl  |> filter(publisher == "Wiley") |> pull(oa_total)) / (publisher_league_tbl  |> filter(publisher == "Wiley") |> pull(publisher_total)) * 100`% of Wiley articles were open acccess), leading to much higher open access market shares (`r publisher_league_tbl  |> filter(publisher == "Springer Nature") |> pull(oa_perc)*100`% Springer Nature resp. `r publisher_league_tbl  |> filter(publisher == "Springer Nature") |> pull(oa_perc)*100`% Wiley).
This  difference can mainly be attributed to transformative agreements, as both publishers made the majority of their open access articles available through such deals (Springer Nature `r ((publisher_league_tbl  |> filter(publisher == "Springer Nature") |> pull(ta_oa_total)) / (publisher_league_tbl  |> filter(publisher == "Springer Nature") |> pull(oa_total)) * 100)`% resp. Wiley `r (publisher_league_tbl  |> filter(publisher == "Wiley") |> pull(ta_oa_total)) / (publisher_league_tbl  |> filter(publisher == "Wiley") |> pull(oa_total)) * 100`%).

Figure 2 presents the growth of hybrid open access across publishers by year, highlighting the growth of open articles published under transformative agreements. As can be seen from Figure 2A and 2C
